Employee Attrition: What makes an employee leave?

### 2017-10-23 LatexPaper/paper.tex
Added manual feature selection section and added potential plots to be discussed in feature importance selection

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{ {Images/} }
\usepackage{float}
\usepackage[backend=bibtex,style=verbose-trad2]{biblatex}
%\bibliography{bib}

@@

\subparagraph{During analysis, dimensionality reduction was performed on the datasets. This was essential to reduce numerous correlating and covariant relationships present between dataset variables. Only after these relationships were addressed and the datasets simplified were the data prepared for modelling.}

@@

\paragraph{The U.S. Office of Personnel Management (OPM) serves as the central Human Resources department for all Federal agencies, including the management of federal agency health insurance and retirement benefits. Their oversight of policy implementation as well as being a general resource for all agency Human Resource departments makes their employment data of particular interest for this paper. OPM releases on a quarterly basis updated separation data on its over two million federal civil service workers.  We used these anonymized data sets to create a full year of separation data, spanning October 2014 - September 2015.   These data [7], include the following variables: 1) age group, captured categorically in 5 year increments (AGELVL and AGELVLT), 2) agency type and subtype information (AGYTYP, AGYTYPT, AGY, AGYT, AGYSUB, and AGYSUBT), 3) gender (GENDER and GENDERT), 4) General Schedule Grade, or equivalent, dictating salary level (GSEGRD, 5) geographical location of the employee down to the state level (LOCTYP, LOCTYPT, LOC, LOCT), 5)length of service as a government employee captured in one year increments until five years was achieved, then every five after that (LOSLVL and LOSLVLT), 6)occupation type  in regards to white or blue collar, occupation family, and in some cases, down to the particular occupation itself (i.e. "chaplain") (OCCTYP, OCCTYPT, OCCFAM, OCCFAMT, OCC, OCCT), 7) occupation category among seven main categories (i.e. "Technical" and "Clerical")(PATCO and PATCOT), 8) pay plan and grade for both GSE and non-GSE occupations (PPTYP, PPTYPT, PPGROUP, PPGROUPT, PAYPLAN, PAYPLANT, and PPGRD), 9) salary range, captured categorically starting with $<$ \$20,000 and followed in \$10,000 increments (SALLVL and SALLVLT), 10) reason for separation (SEP and SEPT), and 11) type of appointment and worschedules, denoting factors such as permanence, seasonality, and executive status (TOATYP, TOATYPT, TOA, TOAT, WSTYP, WSTYPT, WORKSCH, and WORKSCT).   }

@@

\subparagraph{The correlation values for separation from quitting (SEP\_SC) in Fig. 3 is what interests us most.  As paygrade decreases, the likelihood of separation by quitting increases (r = 0.2). This make logical sense, as paygrade is directly tied to income.  However, this correlation also exactly matches the correlation for the salary differential from the industry, so there is not enough direction to say that the status of the paygrade is what matters more so than the actual salary. Though not indicated in Fig. 3, salary and paygrade level do in fact strongly correlate with one another (r = 0.9). As such, the two are most likely one and the same in an employee's mind, and only one of the two will be used for modeling purposes.}

@@

\subparagraph{These 22 principal components were utilized both as a dataset of component vectors as well as to identify the top 15 features within each of the 22 component loading magnitudes. The latter approach reduced our inputs to 49 features, allowing only the most important features to proceed into our model as raw scaled values, based on PCA component loadings.}

\subparagraph{Manual Logistic Regression Feature Selection:[CHRIS TO WRITE A PARAGRAPH ON THIS PROCESS, WHAT VALUES ARE ANALYZED{P VALUE, VIF, ETC.}, AND THRESHOLDS FOR REMOVAL.]
}

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\graphicspath{ {Images/} }
\usepackage{float}
\usepackage[backend=bibtex,style=verbose-trad2]{biblatex}
%\bibliography{bib}

@@

\subparagraph{During analysis, dimensionality reduction was performed on the datasets. This was essential to reduce numerous correlating and covariant relationships present between dataset variables. Only after these relationships were addressed and the datasets simplified were the data prepared for modeling.}

@@

\paragraph{The U.S. Office of Personnel Management (OPM) serves as the central Human Resources department for all Federal agencies, including the management of federal agency health insurance and retirement benefits. Their oversight of policy implementation as well as being a general resource for all agency Human Resource departments makes their employment data of particular interest for this paper. OPM releases, on a quarterly basis, updated separation data on its over two million federal civil service workers.  We used these anonymized data sets to create a full year of separation data, spanning October 2014 - September 2015.   These data [7], include the following variables: 1) age group, captured categorically in 5 year increments (AGELVL and AGELVLT), 2) agency type and subtype information (AGYTYP, AGYTYPT, AGY, AGYT, AGYSUB, and AGYSUBT), 3) gender (GENDER and GENDERT), 4) General Schedule Grade, or equivalent, dictating salary level (GSEGRD, 5) geographical location of the employee down to the state level (LOCTYP, LOCTYPT, LOC, LOCT), 5)length of service as a government employee captured in one year increments until five years was achieved, then every five after that (LOSLVL and LOSLVLT), 6)occupation type  in regards to white or blue collar, occupation family, and in some cases, down to the particular occupation itself (i.e. "chaplain") (OCCTYP, OCCTYPT, OCCFAM, OCCFAMT, OCC, OCCT), 7) occupation category among seven main categories (i.e. "Technical" and "Clerical")(PATCO and PATCOT), 8) pay plan and grade for both GSE and non-GSE occupations (PPTYP, PPTYPT, PPGROUP, PPGROUPT, PAYPLAN, PAYPLANT, and PPGRD), 9) salary range, captured categorically starting with $<$ \$20,000 and followed in \$10,000 increments (SALLVL and SALLVLT), 10) reason for separation (SEP and SEPT), and 11) type of appointment and worschedules, denoting factors such as permanence, seasonality, and executive status (TOATYP, TOATYPT, TOA, TOAT, WSTYP, WSTYPT, WORKSCH, and WORKSCT).   }

@@

\subparagraph{The correlation values for separation from quitting (SEP\_SC) in Fig. 3 is what interests us most.  As paygrade decreases, the likelihood of separation by quitting increases (r = 0.2). This makes logical sense, as paygrade is directly tied to income.  However, this correlation also exactly matches the correlation for the salary differential from the industry, so there is not enough direction to say that the status of the paygrade is what matters more so than the actual salary. Though not indicated in Fig. 3, salary and paygrade level do in fact strongly correlate with one another (r = 0.9). As such, the two are most likely one and the same in an employee's mind, and only one of the two will be used for modeling purposes.}

@@

% Comment(Chris): Missing Top 15 Raw Scaled Features within Each PCA Loading here
\subparagraph{These 22 principal components were utilized both as a dataset of component vectors as well as to identify the top 15 features within each of the 22 component loading magnitudes. The latter approach reduced our inputs to 49 features, allowing only the most important features to proceed into our model as raw scaled values, based on PCA component loadings.}

\subparagraph{Manual Logistic Regression Feature Selection: Important independent variables were identified by first assessing multicollinearity and covariance among the 99 raw features, and then iteratively generating logistic regression models - removing one feature at a time with each iteration. Removal criteria were based on Variance Inflation Factor (VIF) values (Threshold for removal was VIF of 10), Null Deviance, Log Likelihood, Akaike Information Criterion (AIC), Bayesian Information Criterion (BIC), and p-values ($\alpha = 5$). Only statistically significant features remained for model input after completing this process (32 variables in total).}

@@

\subparagraph{}
\begin{figure}
\centering
\subfloat[first]{
  \includegraphics[width=60mm]{Violin_AGELVL_H.pdf}
}
\subfloat[second]{
  \includegraphics[width=60mm]{Violin_AGELVL_G.pdf}
}
\hspace{0mm}
\subfloat[third]{
  \includegraphics[width=60mm]{Violin_AGELVL_I.pdf}
}
\subfloat[fourth]{
  \includegraphics[width=60mm]{Violin_AGELVL_B.pdf}
}
\hspace{0mm}
\subfloat[fifth]{
  \includegraphics[width=60mm]{Violin_AGELVL_F.pdf}
}
\caption{Violin Plots - Significant Age Levels}
\label{fig:ViolinAge}
\end{figure}

\subparagraph{}
\begin{figure}
\centering
\subfloat[first]{
  \includegraphics[width=60mm]{Violin_LOC_46.pdf}
}
\subfloat[second]{
  \includegraphics[width=60mm]{Violin_LOC_30.pdf}
}
\hspace{0mm}
\subfloat[third]{
  \includegraphics[width=60mm]{Violin_LOC_04.pdf}
}
\subfloat[fourth]{
  \includegraphics[width=60mm]{Violin_LOC_06.pdf}
}
\hspace{0mm}
\subfloat[fifth]{
  \includegraphics[width=60mm]{Violin_LOC_20.pdf}
}
\caption{Violin Plots - Significant Locations}
\label{fig:ViolinLoc}
\end{figure}

\subparagraph{}
\begin{figure}
\centering
\subfloat[first]{
  \includegraphics[width=60mm]{Violin_TOA_44.pdf}
}
\subfloat[second]{
  \includegraphics[width=60mm]{Violin_TOA_42.pdf}
}
\hspace{0mm}
\subfloat[third]{
  \includegraphics[width=60mm]{Violin_TOA_20.pdf}
}
\subfloat[fourth]{
  \includegraphics[width=60mm]{Violin_TOA_35.pdf}
}
\caption{Violin Plots - Significant Types of Appointment}
\label{fig:ViolinTOA}
\end{figure}

\subparagraph{}
\begin{figure}[H]
\centering
\includegraphics[width=60mm]{Violin_PPGROUP_11.pdf}
\caption{Violin Plot - Pay Plan Group 11}
\label{fig:ViolinPPGROUP}
\end{figure}

% Comment(Chris): Will likely need to enlarge font size but need to shorten BLS name to do so
\subparagraph{}
\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ScatterMatrix.jpg}
\caption{Scatter Plot Matrix Results for Top Numeric Attributes}
\label{fig:ScatterMatrix}
\end{figure}
